Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-14 qpip0.tex
Add discussion TODOs

By combining the commitment Protocol, $\PiMeasure$, and our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, we get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.
In particular, we combine them by replacing the verifier's measurements with a call to $\PiMeasure$. It is possible because $\VSamp$ applies only $X$ and $Z$ measurements.
Furthermore, its measurements are not adaptive, meaning measurement results do not change later measurement basis choices.

\Ethan{Probably can omit details from below}

@@

\Ethan{Might need to fix the following. Note that it's not a standard parallel rep, so we can't just say it's N-fold parallel rep without saying anything else}

>>>>

By combining the commitment Protocol, $\PiMeasure$, and our $\QPIP_1$ Protocol for $\SampBQP$, $\PiSamp=(\PSamp, \VSamp)$, we get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.
\Ethan{The following discussion is mine}
In particular, we combine them by replacing the verifier's measurements with a call to $\PiMeasure$. It is possible because $\VSamp$ applies only $X$ and $Z$ measurements.
Furthermore, its measurements are not adaptive, meaning measurement results do not change later measurement basis choices.

@@

\Ethan{TODO add discussion about parallel rep}
